---
title: "Workflow"
---

## Data wrangling

### The MLIT Dataset

The data used in this analysis comes from the [MLIT Dataset](https://www.reinfolib.mlit.go.jp/realEstatePrices/), which contains records of real estate price transactions across Japan since 2003.

You can select the prefectures you want to download. I chose to download all of them and ended up with 47 datasets, corresponding to the 47 prefectures of Japan.

### Wrangling the data

I use Stata to combine the 47 datasets and save the big one file as `data_mlit`, since Stata is more convenient for handling encoding issues. Note that it might take some time.

```{stata}
#| eval: false
cd "/Users/anthony/Desktop/master_thesis/data/raw/mlit"

local prefectures : dir "." files "*.csv"
clear

foreach prefecture of local prefectures {
	preserve
	import delimited "`prefecture'", clear
	tempfile temp
	save `temp'
	restore 
	append using `temp'
}

save data_mlit, replace
```

### Importing the data

I go back using R here. The data take a lot of time to load.

```{r}
#| label: package-wrangling
#| code-fold: true
#| code-summary: "Show code to load packages"
#| echo: true
#| message: false
#| warning: false

library(haven)
library(tidyverse)
library(kableExtra)
```

```{r}
#| cache: true
#| eval: false
data_mlit_raw <- read_dta("/Users/anthony/Desktop/master_thesis/data/raw/mlit/data_mlit.dta")
data_mlit <- data_mlit_raw
```

Since loading the data requires a lot of time, I generate also a sample in case, 10% of the initial *data_mlit*.

```{r}
#| eval: false
data_mlit_sample <- data_mlit |>
  slice_sample(prop = 0.1)
```

Let's clean this database!

## Data cleaning

More coding samples will be available soon.

First, I take a look at the data. There are several things that need to be fixed:

-   many cells are missing, whereas there should be NA.

-   totaltransactionvalue should appear clearly as a numerical

-   neareststationdistance is a string

-   etc.

```{r}
data_mlit
```

```{r}
data_mlit |>
  distinct(prefecture)
# We need to retreive "Prefecture" from prefecture
```

Let's first deal with the **missing values**.

```{r}
# Let's first replace empty cells (string and numerical) by NA
data_mlit <- data_mlit |>
  mutate_if(is.character, list(~na_if(.,"")))

# Let's count how many rows contain at least one NA
data_mlit_na <- data_mlit |>
  filter(if_any(everything(), is.na))
```

```{r}
# Example plot
library(ggplot2)
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Car Weight vs MPG")
```

## Analysis

```{r}
library(ggplot2)
```

Look forward for the results!

------------------------------------------------------------------------

[Back to Home](index.html)
